Converging High-Throughput and High-Performance Computing Paradigms: \\ A Case Study of Using Abstractions to Bridge the Divide

### 2017-03-12 PandaEvolution.tex
Address #5

Titan's backfill functionality offers the opportunity not to use the pilot
abstraction while still avoiding queue time overheads. Backfill availability is
the number of work nodes that cannot be used by any of the jobs already queued
on Titan: All queued jobs are either too large or their walltime is too long. At
any point in time, Titan's Moab scheduler can be queried for backfill
availability and a job submitted shortly after placing this query and requesting
for no more than the backfill availability, is usually scheduled immediately
spending almost no time in the queue.

>>>>

Titan’s backfill functionality offers the opportunity to avoid the overhead of
queue wait times without using pilot abstraction. Backfill availability is the
number of work nodes that cannot be used by any of the jobs already queued on
Titan: All queued jobs are either too large or their walltime is too long. At
any point in time, Titan’s Moab scheduler can be queried for backfill
availability. Based upon the result of this query, a job can be shaped to
request no more than the backfill availability, and when submitted as such is
usually scheduled immediately spending almost no time in the queue.
